Equalizer\\Programming and User Guide

### 2010-12-20 Developer/ProgrammingGuide/paper.tex
Fix XCode Makefile rule Remove now-unneeded affinity WAR
[ ] May break build
[ ] May break existing applications (see CHANGES.txt)
[x] Bugfix
[ ] New Feature
[x] Cleanup
[ ] Optimization
[x] Documentation

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_AFFINITY\\
  \textbf{Value} & OFF \textbar \ ON \textbar \ AUTO\textbar \ EXTERN\\
  \textbf{Default} & AUTO\\
  \textbf{Details} & Determines how the window handles the affinity context (WGL
  only). This hint is a workaround for NVidia drivers greater than 200, which
  contain a faulty implementation of the WGL\_NV\_gpu\_affinity extension. When
  set to AUTO, the hint is interpreted like EXTERN for windows and pbuffers with
  these drivers, in all other cases it is interpreted like ON. When set to ON,
  an affinity DC is used for all drawable types. When set to EXTERN, a normal DC
  is used to create the drawable, but an affinity DC is created and can be used
  by the application to render into a FBO. This hint may be ignored in later
  versions of Equalizer, once this workaround has become obsolete.\\
  \hline
\end{tabularx}\\\vfill

@@

For the WGL window system, the device selects the \textit{n}th GPU in
the system. The GPU can be offline, in this case only PBuffer windows
can be used. To restrict the OpenGL output to the GPU, the
\textsf{WGL\_NV\_gpu\_affinity} extension is used. If the extension is
not present, the window is opened on the \textit{n}th monitor, but
OpenGL commands are sent to all GPU's.

@@

    attributes
    {
        hint_affinity       OFF | ON | AUTO | EXTERN
        hint_stereo         OFF | ON | AUTO
        hint_doublebuffer   OFF | ON | AUTO
        hint_decoration     OFF | ON
        hint_fullscreen     OFF | ON
        hint_swapsync       OFF | ON         # AGL, WGL only
        hint_drawable       window | pbuffer | FBO
        hint_statistics     off | fastest [on] | nicest
        planes_color        unsigned | RGBA16F | RGBA32F
        planes_alpha        unsigned
        planes_depth        unsigned
        planes_stencil      unsigned
        planes_accum        unsigned
        planes_accum_alpha  unsigned
        planes_samples      unsigned
    }

>>>>

@@

For the WGL window system, the device selects the \textit{n}th GPU in
the system. The GPU can be offline, in this case only PBuffer windows
can be used. To restrict the OpenGL output to the GPU, the
\textsf{WGL\_NV\_gpu\_affinity} extension is used. If the extension is
not present, the window is opened on the \textit{n}th monitor, but
OpenGL commands are sent to a different or all GPU's.

@@

    attributes
    {
        hint_stereo         OFF | ON | AUTO
        hint_doublebuffer   OFF | ON | AUTO
        hint_decoration     OFF | ON
        hint_fullscreen     OFF | ON
        hint_swapsync       OFF | ON         # AGL, WGL only
        hint_drawable       window | pbuffer | FBO
        hint_statistics     off | fastest [on] | nicest
        planes_color        unsigned | RGBA16F | RGBA32F
        planes_alpha        unsigned
        planes_depth        unsigned
        planes_stencil      unsigned
        planes_accum        unsigned
        planes_accum_alpha  unsigned
        planes_samples      unsigned
    }
